Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-22 paper/supplemental/architecture.tex

\subsection{CNN Architecture}
2 vs 4 layers vs resnet

>>>>

\subsection{Architecture}
We explored different architectures for the convolutional neural network (CNN) for split error detection. In table \ref{tab:architecture} we compare traditional CNN architectures versus residual networks~\cite{resnet}. The traditional architecture generalized better than residual networks on unseen testing data.

\begin{table}[h]
\caption{Traditional CNN Architecture versus Residual Network Architecture \cite{resnet}. All configurations are compared using the same parameters. Our final choice (indicated by *) trains relatively fast and performs better.}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{@{}ll|l@{}}
	\toprule
     ~ & \textbf{Traditional Network} & \textbf{Residual Network}  \\ \midrule	
\begin{tabular}{@{}r|@{}}
Conv. Layers \\
Dropout Reg. \\
Cost [m] \\
Test. Acc. \\
Prec./Recall \\
F1 Score\\
~
\end{tabular} & 
\begin{tabular}{@{}c|c@{}}
 2 & 4 \\
 y & y \\
 27.5 & 383 \\
 0.925 & 0.94 \\
 0.93/0.93 &
 0.94/0.94 \\
 0.93 & 0.94 \\
 ~&*
\end{tabular}
& 
\begin{tabular}{@{}c|c@{}}
 5 & 13 \\
 y & n \\
5080 & 1094 \\
 0.93 & 0.90 \\
 0.7/0.53 &
 0.74/0.66 \\
 0.39 & 0.64\\
 ~&~

\end{tabular}

\end{tabular}
\hspace{2mm}
\hrule
}
\label{tab:architecture}
\end{table}
